Without loss of generality, \\ any reduced ring is a field

### 2020-04-02 paper-herrsching2019/main.tex
Semantics of relation symbols

\begin{table}[ht]
  \tbl{The (first-order fragment of) the sheaf semantics of a locale~$X$}{\begin{tabular}{@{}l@{\ \ }c@{\ \ }l@{}}
    $U \models s =_F t$ &\Ll& $s = t$ when evaluated as elements of~$F(U)$ \\
    $U \models \top$ &\Ll& true \\
    $U \models \varphi \wedge \psi$ &\Ll& $U \models \varphi$ and $U \models \psi$ \\
    $U \models \bot$ &\Ll& \hcancel{false}{0pt}{3pt}{0pt}{-2pt}\ $U = \bot$ \\
    $U \models \varphi \vee \psi$ &\Ll& \hcancel{$U \models \varphi$ or $U \models \psi$}{0pt}{3pt}{0pt}{-2pt}\ there exists an open covering $U = \bigvee_i U_i$ \\
    && \quad\quad such that for all~$i$: $U_i \models \varphi$ or $U_i \models \psi$ \\
    $U \models \varphi \Rightarrow \psi$ &\Ll& for all~$V \preceq U$: $V \models \varphi$ implies $V \models \psi$ \\
    $U \models \forall s \? F\_ \varphi(s)$ &\Ll& for all $V \preceq U$ and sections~$s_0 \in F(V)$: $V \models \varphi(s_0)$ \\
    $U \models \exists s \? F\_ \varphi(s)$ &\Ll& \hcancel{there exists $s_0 \in F(U)$ such that $U \models \varphi(s_0)$}{0pt}{3pt}{0pt}{-2pt} \\
    && there exists an open covering $U = \bigvee_i U_i$ such that for all~$i$: \\
    && \quad\quad there exists~$s_0 \in F(U_i)$ such that $U_i \models \varphi(s_0)$
  \end{tabular}}
  \label{table:sheaf-semantics}
\end{table}

>>>>

\begin{table}[ht]
  \tbl{The (first-order fragment of) the sheaf semantics of a locale~$X$}{\begin{tabular}{@{}l@{\ \ }c@{\ \ }l@{}}
    $U \models s =_F t$ &\Ll& $s = t$ when evaluated as elements of~$F(U)$ \\
    $U \models R(s_1,\ldots,s_n)$ &\Ll& $\langle s_1,\ldots,s_n \rangle \in R(U)$ \\
    $U \models \top$ &\Ll& true \\
    $U \models \varphi \wedge \psi$ &\Ll& $U \models \varphi$ and $U \models \psi$ \\
    $U \models \bot$ &\Ll& \hcancel{false}{0pt}{3pt}{0pt}{-2pt}\ $U = \bot$ \\
    $U \models \varphi \vee \psi$ &\Ll& \hcancel{$U \models \varphi$ or $U \models \psi$}{0pt}{3pt}{0pt}{-2pt}\ there exists an open covering $U = \bigvee_i U_i$ \\
    && \quad\quad such that for all~$i$: $U_i \models \varphi$ or $U_i \models \psi$ \\
    $U \models \varphi \Rightarrow \psi$ &\Ll& for all~$V \preceq U$: $V \models \varphi$ implies $V \models \psi$ \\
    $U \models \forall s \? F\_ \varphi(s)$ &\Ll& for all $V \preceq U$ and sections~$s_0 \in F(V)$: $V \models \varphi(s_0)$ \\
    $U \models \exists s \? F\_ \varphi(s)$ &\Ll& \hcancel{there exists $s_0 \in F(U)$ such that $U \models \varphi(s_0)$}{0pt}{3pt}{0pt}{-2pt} \\
    && there exists an open covering $U = \bigvee_i U_i$ such that for all~$i$: \\
    && \quad\quad there exists~$s_0 \in F(U_i)$ such that $U_i \models \varphi(s_0)$
  \end{tabular}}
  \label{table:sheaf-semantics}
\end{table}
